---
title: "Experiments cross-referencing, simplified for just getting what is needed"
author: "Thell 'Bo' Fowler (Thell) modifs by Bruno Fischer Colonimos"
date: "16 juillet 2017"
output:
  html_document:
    fig_cap: yes
    keep_md: yes
  pdf_document: 
    fig_cap: yes
---

# First, some hidden code {#sec:code}


```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE, fig.pos = "H", fig.cap = "") 
```

**Main code chunks** 

```{r setup2, echo=FALSE, results='hide'}

library(ggplot2)

# reference functions

chunkref <- local({
  function(chunklabel) {
    sprintf('[%s](#%s)', chunklabel, chunklabel )
  }  
})

secref <- local({
  function(seclabel) {
    sprintf('[%s](#%s)', seclabel, seclabel )
  }  
})

pgref <- local({
  function(n)
  sprintf('[Page-%i](#Page-%i)', n, n)
})

# added*****************************

# From Hadley's ggplot2 book:  Knowing conversion target 
is_latex <- function() {
        identical(knitr::opts_knit$get("rmarkdown.pandoc.to"), "latex")
}

# html same
is_html <- function() {
        identical(knitr::opts_knit$get("rmarkdown.pandoc.to"), "html")
}

pdfoutput <- is_latex() # tells if we are converting through latex, ie to pdf

# getcontext returns the doc conversion context
getcontext <- function(){
        if (is_latex()) {"latex" 
                   } else if (is_html()) {
                           "html"
                   } else {"other"} 
}


# get the code chunk name (for captionning)

getchunkname <- function() {knitr::opts_current$get("label")}

figref <- local({
  function(figlabel) {
    sprintf('[%s](#%s)', figlabel, figlabel )
  }  
})

figcap <- local({
  function(captext, figlabel = paste0("fig:", getchunkname())) {
    sprintf('<a name="%s"></a>%s', figlabel, captext )
  }  
})

tabcap <- local({
  function(captext, figlabel = paste0("tab:", getchunkname())) {
    sprintf('<a name="%s"></a>%s', figlabel, captext )
  }  
})


# test
# cat(figcap("Le texte", "etiquette"))


# creating the labels/anchors
sec <- local({
  function(seclabel) {
    sprintf('# <a name="%s"/> %s', seclabel, seclabel )
  }  
})

pgcount <- local({
  pg <- 0
  function(inc=T) {
    if( inc ) { pg <<- pg + 1 }
    return( pg )
  }
})

pganchor <- local({
  function(doLabel=T) {
    if( doLabel) {
      sprintf('\n-----\nPage-%i\n<a name="Page-%i"/>\n', pgcount(inc=F), pgcount() )
    } else {
      sprintf('\n<a name="Page-%i"/>\n', pgcount() )
    }
  }
})

# hooks *************
# 
# knitr::knit_hooks$set( anchor = function(before, options, envir) {
#   if ( before ) {
#     sprintf('<a name="%s"/>\n', options$label )
#   }
# })
# 
# knitr::knit_hooks$set( echo.label = function(before, options, envir) {
#   if ( before ) {
#     sprintf('> %s', options$label )
#   }
# })
# 
# knitr::knit_hooks$set( pgbreak = function(before, options, envir) {
#   if ( !before ) {
#     pganchor()
#   }
# })

```

found at :https://gist.github.com/Thell/5827832#file-exmple-rmd



# Introduction {#sec:intro}

All things are possible!  Later in this document the `r secref("knitr-setup")` listing describes some possible ways things can be accomplished.

For now, let us imagine that we have a solution chunk which we will later refer to:

```{r Solution1, eval=FALSE}
# removed , anchor=T, echo.label=T
data(cars)
car_summary<-summary(cars)
```

Followed by a chunk that generates some image...

```{r carplot, echo=TRUE, fig.cap = "One Figure"}
# removed fig.cap=figcap("One Figure") , warning=FALSE, anchor=TRUE

ggplot(cars, aes(x = speed, y=dist )) + geom_jitter()

```


I didn't bother figuring out why fig.cap wasn't inserted in the html rendering, but since that isn't what is being described here let's just move on...

This following chunk's noisy output, even though `quietly=T` and `warning=F` is annoying but the table is output just fine.  It illustrates what can be done with the output from `r secref("Solution1")`.

```{r carsummary, echo=T}
# removed , warning=FALSE, anchor=T, pgbreak=T, echo.label=F
library(pander, quietly=T)
car_summary<-summary(cars)
pander(car_summary, caption = tabcap("This is a summary of cars"))
```

some text.






# Hooks {#sec:Hooks}


This is made possible using hooks and R functions like these: ()

```{r knitr-setup, ref.label="setup", echo=TRUE, eval = FALSE, results='asis' }
```



```
`r figref("fig:carplot" )`


As previously mentioned ( `r secref("sec:intro")` ), _anything is do-able_  


# The question is:


* Do you really think markdown is the right tool to use if you want to see `r chunkref("Solution-1")`, the `r chunkref("car-plot")`, or the `r chunkref("car-summary")`?  It could be especially questionable to jump to the top of `r pgref(1)` or `r pgref(2)`.

what about referencing ; `r figref(fig:car_summary)  `

```
 

