---
title: "Experiments cross-referencing"
author: "Thell 'Bo' Fowler (Thell) modifs by Bruno Fischer Colonimos"
date: "9 juillet 2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup0, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```


```{r setup, echo=FALSE, results='hide'}
chunkref <- local({
  function(chunklabel) {
    sprintf('[%s](#%s)', chunklabel, chunklabel )
  }  
})

secref <- local({
  function(seclabel) {
    sprintf('[%s](#%s)', seclabel, seclabel )
  }  
})

pgref <- local({
  function(n)
  sprintf('[Page-%i](#Page-%i)', n, n)
})

sec <- local({
  function(seclabel) {
    sprintf('# <a name="%s"/> %s', seclabel, seclabel )
  }  
})

pgcount <- local({
  pg <- 0
  function(inc=T) {
    if( inc ) { pg <<- pg + 1 }
    return( pg )
  }
})

pganchor <- local({
  function(doLabel=T) {
    if( doLabel) {
      sprintf('\n-----\nPage-%i\n<a name="Page-%i"/>\n', pgcount(inc=F), pgcount() )
    } else {
      sprintf('\n<a name="Page-%i"/>\n', pgcount() )
    }
  }
})

knitr::knit_hooks$set( anchor = function(before, options, envir) {
  if ( before ) {
    sprintf('<a name="%s"/>\n', options$label )
  }
})

knitr::knit_hooks$set( echo.label = function(before, options, envir) {
  if ( before ) {
    sprintf('> %s', options$label )
  }
})

knitr::knit_hooks$set( pgbreak = function(before, options, envir) {
  if ( !before ) {
    pganchor();
  }
})

````

found at :https://gist.github.com/Thell/5827832#file-exmple-rmd

`r pganchor(F)`
`r sec("Introduction")`

All things are possible!  Later in this document the `r secref("knitr-setup")` listing describes some possible ways things can be accomplished.

For now, let us imagine that we have a solution chunk which we will later refer to:

```{r Solution-1, eval=FALSE, anchor=T, echo.label=T}
car_summary<-summary(cars)
```

Followed by 'hidden' chunk that generates some image...

```{r car-plot, echo=F, fig.cap="car-plot", warning=FALSE, anchor=T}
plot(cars)
```

I didn't bother figuring out why fig.cap wasn't inserted in the html rendering, but since that isn't what is being described here let's just move on...

This following chunk's noisy output, even though `quietly=T` and `warning=F` is annoying but the table is output just fine.  It illustrates what can be done with the output from `r secref("Solution-1")`.

```{r car-summary, echo=T, warning=FALSE, anchor=T, pgbreak=T, echo.label=F}
library(pander, quietly=T)
car_summary<-summary(cars)
pander(car_summary, caption = "This is a summary of cars")
```


`r sec("Hooks")`


This is made possible using hooks and R functions like these:

```{r knitr-setup, ref.label="setup", echo=TRUE, eval=FALSE, results='markup', echo.label=T}
```


__Like previously mentioned ( `r secref("Introduction")` ), _anything is do-able_.__  


### The question is,

> Do you really think markdown is the right tool to use if you want to see `r chunkref("Solution-1")`, the `r chunkref("car-plot")`, or the `r chunkref("car-summary")`?  It could be especially questionable to jump to the top of `r pgref(1)` or `r pgref(2)`.

`r pganchor()`
.
 

