---
title: "minimal file for HTML"
author: BFC
Date: "16/07/17"
lof: yes
output:
  html_document:
    fig_cap: yes
    num_sections: yes
    toc: yes
    keep_md: yes
---


```{r setup}
library(pander)
library(knitr)
library(ggplot2)

# From Hadley's ggplot2 book:  Knowing conversion target 
is_latex <- function() {
        identical(knitr::opts_knit$get("rmarkdown.pandoc.to"), "latex")
}

# html same
is_html <- function() {
        identical(knitr::opts_knit$get("rmarkdown.pandoc.to"), "html")
}


getcontext <- function(){
        if (is_latex()) {"latex" 
                   } else if (is_html()) {
                           "html"
                   } else {"other"} 
}

figcap <- function(caption,
                   chunklabel=knitr::opts_current$get("label"),
                   context=getcontext()) {

        switch(context,
               latex = paste0("\\label{fig:", chunklabel, "}",
                              caption),
               html = paste0("<div id=fig:", chunklabel, ">",
                             caption, "</div>"),
               other = caption )
}


knitr::opts_chunk$set(echo = TRUE, fig.pos = "H", fig.width = 3, fig.asp=0.75, fig.align = "center", fig.cap = figcap(" ")) 
```


```{r firstcode}



# From Hadley's ggplot2 book:  Knowing conversion target 
is_latex <- function() {
        identical(knitr::opts_knit$get("rmarkdown.pandoc.to"), "latex")
}

# html same
is_html <- function() {
        identical(knitr::opts_knit$get("rmarkdown.pandoc.to"), "html")
}

pdfoutput <- is_latex() # tells if we are converting through latex, ie to pdf

# getcontext returns the doc conversion context
getcontext <- function(){
        if (is_latex()) {"latex" 
                   } else if (is_html()) {
                           "html"
                   } else {"other"} 
}


# get the code chunk name (for captionning)

chunkname <- function() {knitr::opts_current$get("label")}


# captions

tabcap <- function(caption,
                   chunklabel=knitr::opts_current$get("label"),
                   context=getcontext()) {

        switch(context,
               latex = paste0("\\label{tab:", chunklabel, "}",
                              caption),
               html = paste0("<div id=tab:", chunklabel, ">",
                             caption, "</div>"),
               other = caption )
}

figcap <- function(caption,
                   chunklabel=knitr::opts_current$get("label"),
                   context=getcontext()) {

        switch(context,
               latex = paste0("\\label{fig:", chunklabel, "}",
                              caption),
               html = paste0("<div id=fig:", chunklabel, ">",
                             caption, "</div>"),
               other = caption )
}

# reference

ref <- local({
  function(label) {
    sprintf('[%s](#%s)', label, label )
  }  
})




```

# Intro {#intro}
Just a test 


# reference before txt {#refbefore}

Ok. Now let us refer: before creation

* plot : `r ref("fig:mtplot")`
* table: `r ref("tab:headchunk")`
* table: `r ref("tab:sumdchunk")`
* headers:  `r ref("intro")` , `r ref("refbefore")` , `r ref("creation")`, `r ref("refafter")`




# creation of material {#creation} 


define a plot
```{r firstchk}
data("mtcars")
colnames(mtcars)
summary(mtcars[, 1:5])

```

```{r mtplot, fig.cap=figcap("this is plot mtcars 1")}
# rem : , fig.cap=figcap("this is plot mtcars 1")
ggplot(mtcars, aes(hp, mpg)) + geom_point()
```

now prnt a table

```{r headchunk}
kable(head(mtcars[, 1:4]), caption = tabcap("this is the head of mtcars"))
```


How is that ??


```{r sumchunk}
kable(summary(mtcars[, 1:4]), caption = tabcap("this is the summary of mtcars"))
```


# reference after creation {#refafter}

Ok. Now let us refer: after creation

* plot : `r ref("fig:mtplot")`
* table: `r ref("tab:headchunk")`
* table: `r ref("tab:sumdchunk")`
* headers:  `r ref("intro")` , `r ref("refbefore")` , `r ref("creation")`, `r ref("refafter")`
