---
title: "Cross refs, captions + figures with Latex/Pdf documents"
author: "Bruno Fischer Colonimos"
date: "11 juillet 2017"
include_graphics: yes
linkcolor: red
lof: yes
lot: yes
output: 
  pdf_document:
    fig_caption: yes
    toc: yes

---


****************
 \ 
 \ 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 3, fig.height=2, fig.align = "center", fig.show = "hold")
```


```{r libs}
library(ggplot2)
library(knitr)
library(pander)
library(xtable)
```


# Objective

Find hard-coded ways to cross-refs. 
Here all is in Latex


# Conclusions

* figures
    * do not need a "Label" in their captions, 
    * are crossreferencable, as soon as they have a caption option in the chunk.
    (i.e. fig.cap = "some text" creates the reference. The anchor name is the chunk name)
    * What if they are supplied a different name ??
    
* tables
    * do need a label command in their captions
    * If a table is create without a caption, the table index is still incremented: if captions are enabled, it is better to systematically caption all tables. 


# Including / referencing  Plots and table examples

You can embed and reference plots, 


## Referencing elements produced later in the document 

Let us reference them before we create them: for example:

* We first have 
    * an uncaptioned kable table in chunk firsttbchunk: table \ref{tab:firsttbchunk}
    * an uncaptioned pander table in chunk firsttb2chunk: table \ref{tab:firsttb2chunk}    
    * an uncaptioned plot figure \ref{fig:firstchunk}, (chunk name as anchor)

    * a text-captioned (without label) plot figure \ref{fig:secchunk}, (chunk name as anchor), and 
    * a text-captioned plot from an unnamed chunk : \ref{fig:unnamed-chunk-1} (chunk name as anchor)

* Regular captioned figures:
    * Figure \ref{fig:pressure} (using chunk name as anchor)
    * Figure \ref{fig:foo} or 
    * figure \ref{fig:fee}  and at last 
    * figure \ref{fig:faa}


* Referencing the tables : 
    * Table \ref{tab:firsttbchunk},
    * Table \ref{tab:firsttb2chunk},
    * table \ref{tab:mtcars}, 
    * table \ref{tab:cars}



## Creating Plots and tables

### One table and more plots

```{r firsttbchunk}
data("ToothGrowth")
kable(head(ToothGrowth), caption = "hehe")
```

```{r firsttb2chunk}
pander(head(faithful), caption = "hoho")
```

```{r firstchunk}
ggplot(ToothGrowth, aes(dose,len, color=supp))+ geom_jitter()
```


```{r secchunk, fig.cap="text capped figure from secchunk"}
ggplot(ToothGrowth, aes(dose,len, color = supp))+ geom_jitter() + facet_grid(. ~ supp)
```


```{r , fig.cap="text capped figure from unknown"}
ggplot(ToothGrowth, aes(dose,len, color = supp))+ geom_jitter() + facet_grid(supp ~ .)
```



```{r pressure, echo=FALSE, fig.cap = "hard-coded"}
# removed:"\\label{fig:foo}This is caption fig 0"
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


```{r foo, fig.cap = "caption fig 1"}
ggplot(mtcars, aes(wt, mpg))+ geom_point()
```


```{r fee, fig.cap = "\\label{fig:fee}This is caption fig 2" }
ggplot(mtcars, aes(cyl, mpg))+ geom_boxplot(aes(group=cyl))
```

Some more text to separate items the, a ast plot

```{r chunfkfaa, fig.cap = "\\label{fig:faa}This is caption fig 3"}
ggplot(mtcars, aes(disp, mpg))+ geom_point(aes(color=factor(cyl)))

```

### More Tables:

You can have tables like this:

```{r mtcars}
kable(head(mtcars[, 1:5]), 
      caption = "\\label{tab:mtcars}This is the 'mtcars' `kable` table (ie 1)")
      
```


Or another: 

```{r cars}
kable(summary(cars), 
      caption = "\\label{tab:cars}This is the 'cars' `kable` table (ie 2)")
```

And another


```{r xcars}
xtable(summary(cars), 
      caption = "\\label{tab:xcars}This is the 'cars' `Xtable` table (ie 3)")
```



## Referencing again after the creation:


And you can also reference figures again:  


* we first have 
    * an uncaptioned plot figure \ref{fig:firstchunk}, 
    * and an uncapped table in the same  chunk: table \ref{tab:firsttbchunk}
    * a text-captioned (without label) plot figure \ref{fig:secchunk}, (chunk name as anchor), and 
    * a text-captioned plot from an unnamed chunk : \ref{fig:unnamed-chunk-1} (chunk name as anchor)

* Regular captioned figures:
    * Figure \ref{fig:pressure} (using chunk name as anchor)
    * Figure \ref{fig:foo} or 
    * figure \ref{fig:fee}  and at last 
    * figure \ref{fig:faa}


Referencing the tables : 

    * Table \ref{tab:firsttbchunk}, 
    * table \ref{tab:mtcars}, 
    * table \ref{tab:cars}


# The end

And some text to finish: 
**Goodbye!**
