---
title: "Cross refs, captions + figures with HTML"
author: "Bruno Fischer Colonimos"
date: "11 juillet 2017"
output: 
  html_document:
    fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 3, fig.height= 2.5, fig.align = "center")
```


```{r libs}
library(ggplot2)
library(knitr)

```


## Objective

Find hard-coded ways to cross-refs. 

Here all is in Hard-coded HTML

## Including / referencing  Plots and table

You can embed and reference plots, for example: plot <A HREF=fig:foo>Figure 1</A>, or plot <A HREF=fig:fee>Figure 2</A>  and at last <A HREF=fig:faa>Figure 3</A>

Referencing the tables : <A HREF=#tab:mtcars> Table 1</A>, <A HREF=#tab:cars> Table 2</A>

### Plots

```{r pressure, echo=FALSE, fig.cap = "Hard Text, no auto num"}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


```{r foo, fig.cap = "<a name=fig:foo></a>This is caption 1" }
ggplot(mtcars, aes(wt, mpg))+ geom_point()
```


```{r fee, fig.cap = "<a name=fig:fee></a> This is caption 2" }
ggplot(mtcars, aes(cyl, mpg))+ geom_boxplot(aes(group=cyl))
```

Some more text to separate items the, a ast plot

```{r chunkfaa, fig.cap = "<a name=#fig:faa></a> This is caption 3" }
ggplot(mtcars, aes(disp, mpg))+ geom_point(aes(color=factor(cyl)))

```

### Tables:

You can have tables like this:

```{r mtcars}
kable(head(mtcars[, 1:5]), 
      caption = "<a name=tab:mtcars>Table 1: This is the 'mtcars' `kable` table</a>")
      
```


Or else:

```{r cars}
kable(summary(cars), 
      caption = "<a name=tab:mtcars>Table 2: This is the 'cars' `kable` table</a>")
```


an you can also reference figures again: plot <A HREF=#fig:foo>Figure 1</A>, or plot <A HREF=#fee>Figure 2</A>  and at last <A HREF=#faa>Figure 3</A>

You can embed and reference plots, for example: plot <A HREF=fig:foo>Figure 1</A>, or plot <A HREF=fig:fee>Figure 2</A>  and at last <A HREF=fig:faa>Figure 3</A>

Referencing the tables : <A HREF=#tab:mtcars> Table 1</A>, <A HREF=#tab:cars> Table 2</A>

And some text to finish: Goodbye!
